Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI~837: A Young Validated Planet in IC~2602

### 2020-07-25 paper/ms.tex
update manuscript
Co-authored-by: Alan Levine <aml@space.mit.edu>

\title{
  Cluster Difference Imaging Photometric Survey (CDIPS) II.
  TOI$\,$837: A Young Validated Planet in IC~2602
}

@@

Finding and studying systems undergoing these evolutionary changes is
a major goal in contemporary exoplanet research.  To identify stars
younger than say 1$\,$Gyr, a number of direct and indirect methods are
available \citep{soderblom_ages_2010}.  The traditional approach is to
isochronally age-date coeval groups of stars, hereafter ``clusters''
\citep[{\it
e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
Young field stars can also be identified isochronally, provided that
they are sufficiently massive \citep{berger_gaia-kepler_2020}.  Other
age indicators include stellar rotation periods, the abundance of
photospheric lithium, and chromospheric diagnostics such as calcium
emission and broadband UV emission.  Studies by for instance
\citet{david_discovery_2018} and G{.}~Zhou et al{.}~(2020, submitted)
have combined these methods to age-date individual field stars hosting
transiting planets.  Many of these latter methods were summarized by
\citet{mamajek_improved_2008}, and have since been calibrated by {\it
e.g.},
\citet{irwin_rotational_2009,barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
and \citet{curtis_tess_2019} for stellar rotation,
\citet{zerjal_chromospherically_2017} for chromospheric activity, and
{\it e.g.}, \citet{berger_identifying_2018} and
\citet{zerjal_galah_2019} for lithium abundances.

@@

The discoveries made by K2 through its surveys of Taurus, the Hyades,
Praesepe, and Upper Sco were a major inspiration for the present work
\citep[{\it
e.g.},][]{Mann_K2_25_2016,obermeier_k2_2016,Mann_et_al_2017,vanderburg_zeitVII_2018,ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018,rizzuto_zeitVIII_2018,livingston_k2-264_2019}.
Observations with K2 convincingly showed that at least some close-in
planets must form within about 10 Myr
\citep{Mann_K2_33b_2016,David_et_al_2017}.  They also led to the first
hints that young planets in clusters may in fact be qualitatively
different from their field counterparts.  For instance, based on its
observed mass, radius, and UV environment, the 700$\,$Myr K2-100b is
probably actively losing its atmosphere, and should become a bare
rocky planet over the next few hundred Myr
\citep{Mann_et_al_2017,barragan_radial_2019}.  The four transiting
planets around V1298~Tau (23$\,$Myr) are also likely to be actively
photoevaporating, and could represent a precursor to Kepler's compact
multiple systems \citep{david_four_2019,david_warm_2019}.

With the aim of advancing the young planet census, we have been using
data from the TESS spacecraft \citep{ricker_transiting_2015} to
perform a Cluster Difference Imaging Photometric Survey
\citep[CDIPS;][]{bouma_cluster_2019}.  Our targets in this survey are
candidate young stars that have been reported in the literature.  At
the time writing, of order $6\times10^5$ light curves from the first
year of TESS observations have been reduced, and are available at
MAST\footnote{\stscilink} through \datasetlink.  Searching these light
curves yielded the candidate transiting planet, \pn, that is the
subject of this analysis.

The transits of \pn\ are grazing, which is a cause for concern.
Particularly for a target near the galactic plane ($b=-5.8^\circ$),
background eclipsing binaries are a major source of astrophysical
false positives \citep[{\it e.g.},][Figure~30]{Sullivan_2015}.  Our
follow-up data show that this and related scenarios are unlikely to
the degree that we can ``validate'' the planet, {\it i.e.}, rule that
its probability of being an astrophysical false positive is negligibly
small.  We considered this result worth reporting because of the
planet's youth.

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.77\textwidth]{f2a.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf TESS light curve of \tn.}
    {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Starspot-induced variability is the dominant signal; flares are
    shown with gray crosses.  Dashed lines indicate the five transits
    observed by TESS over Sectors 10 and 11.  {\it Middle}: Individual
    transits.  Gray lines are the best-fit transit model, which
    includes a local quadratic trend in each window. Gray points are
    2-minute \texttt{PDCSAP} flux measurements, black points are
    binned to 15-minute intervals.  {\it Bottom}: Phase-folded TESS
    transit.  Gray points are 2-minute measurements with the local
    spot-induced variation removed.  Black points are binned to
    6-minute intervals.  The black error-bar shows the median
    uncertainty for the black points.  The gray line shows the
    best-fit model to the TESS data. 
		\label{fig:tessphot}
	}
\end{figure*}

@@

The TESS project detected the transits in the 2-minute data and the
community was alerted on 17 June 2019.  While our CDIPS FFI light
curves also showed the transits, the 2-minute data had better sampling
cadence, and so we opted to use the Presearch Data Conditioning (PDC)
light curve with the default aperture for our
analysis~\citep{smith_kepler_2012,stumpe_multiscale_2014,jenkins_tess_2016,smith_finding_2016}.

@@

The Gaia imaging, reduced to its point-source catalog, provides the
initial context for analyzing the TESS data.  Stars brighter than
$T=16$, as queried from the Gaia DR2 source catalog, are shown with
white circles in Figure~\ref{fig:scene}, overlaid on the TESS image.
Given its galactic latitude of $b=-6^\circ$, it is not surprising that
the field of \tn\ is crowded.  The resolved stars that were of
immediate concern for our false positive analysis were as follows.
\begin{itemize}
  %
  \item \tn\ $\equiv$ TIC 460205581 ($T=9.9$). The target star.
  %
  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3''$ West. The
    proper motions and parallax of this star imply it is co-moving with
    \tn\ and that the two stars are separated by $6.6\pm 0.1\,{\rm pc}$.
    Star A is therefore likely an \cn\ member, but unlikely to be a bound
    binary companion.
  %
  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4''$ North.  The
    Gaia parallax implies this is a giant background star.
\end{itemize}
An additional source, TIC 847769581, is $4.9''$ from the target, but
too faint ($T=18.8$) to be the source of the observed transit signal.

@@

At the $\approx1'$ resolution of the TESS data, if either Star A or
Star B were eclipsing binaries, they could be the sources of the
transit signal.  A detailed analysis of ground-based seeing-limited
photometry was necessary to assess and rule out this possibility
(Section~\ref{subsec:groundphot}).

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.49\textwidth]{f2b.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Ground-based follow-up photometry.} The data were acquired
    using the 0.36$\,$m at El Sauce and the 0.40$\,$m ASTEP400 at Dome
    C.  Black points are binned to 10-minute intervals.  The gray line
    is the best-fit model to the combined TESS and ground-based data.
    Red and blue lines show 2-$\sigma$ lower limits on the transit
    depths in the Cousins-R and Johnson-B bandpasses used to rule out
    specific false positive scenarios (see
    Section~\ref{subsec:colorphot}).
		\label{fig:groundphot}
	}
\end{figure}

@@

\tn\ was observed with ASTEP on 12 May 2020, 29 May 2020, 14 June
2020, and 23 June 2020 (UT) with a cadence of $50\,$s (exposure time
of $25\,$s, readout and processed overhead of $25\,$s).  Except for 12
May, our observations were conducted under stable weather conditions,
with clear skies, temperatures of about $-70^\circ$C, and wind speeds
less than 5\,ms$^{-1}$. Due to their poor quality, we exclude from the
analysis all data collected on May 12. We found that the optimal
calibrated light curves of \tn\ correspond to an 11 pixel (10\,arcsec)
and 14 pixel (12\,arcsec) radius aperture for observations carried out
on June and May, respectively.  The data are reported in
Table~\ref{tab:phot}, and plotted in Figure~\ref{fig:groundphot}.

@@

The spectroscopic line profiles were thoroughly examined for any signs
of secondary lines that might indicate the presence of another star,
either associated or in chance alignment with TOI 837. No such set of
lines were found. To determine our detection limits to a blended
spectroscopic companion, we injected a second set of lines to the mean
least-squares deconvolution profile derived from the CHIRON
observations. The injection spanned 10,000 different combinations of
line broadening, velocity separation, and flux ratio $F_2/F_1$. The
recovery results showed that for rotational broadenings of the
secondary of $5$, $15$, and $25\,\mathrm{km\,s}^{-1}$, we were able to
exclude sources with flux fractions $F_2/F_1$ brighter than roughly
$0.03$, $0.08$, and $0.20$, provided that the secondary was separated
from the primary by at least $\approx 15\,{\rm km\,s}^{-1}$.  At
smaller velocity separations, the injected lines begin to blend with
the target spectrum.

\subsubsection{FEROS}
TOI 837.01 was monitored with the FEROS echelle spectrograph
\citep{kaufer_commissioning_1999}, mounted on the MPG 2.2$\,$m
telescope at the ESO La Sille Observatory, in Chile. FEROS has a
resolution of $\approx$48,000 across a spectral range of 350–920 nm.
It has a remarkably high efficiency of $\approx$20\%. We obtained 13
spectra of \tn\ between July 5 of 2019 and March 14 of 2020 in the
context of the Warm gIaNts with tEss (WINE) collaboration, which
focuses on the systematic characterization of TESS transiting giant
planets with moderately long orbital periods \citep[{\it
e.g.},][]{brahm:2019,jordan:2020}.  We adopted exposure times of 500
and 600 seconds and the observations were performed with the
simultaneous calibration mode for tracing the instrumental velocity
variations with a comparison fiber illuminated with a ThAr lamp. FEROS
data was processed with the \texttt{ceres} pipeline
\citep{brahm_2017_ceres}, which delivers precision radial velocities
and bisector span measurements through cross-correlation of the
extracted spectra with a binary mask resembling the properties of a
G2V star. The radial velocities are given in Table~\ref{tab:rvs}, and
shown in Figure~\ref{fig:followup}.
To check for the presence of secondary lines, we performed a similar
injection-recovery exercise as with the CHIRON data. 
We achieved slightly worse limits, likely due to the lower spectral
resolution of FEROS, and therefore adopted the CHIRON limits.

@@

Validating a transiting planet means statistically arguing that the
data are much more likely to be explained by a planet than by an
astrophysical false positive. The concept of validation has been
developed and calibrated by {\it e.g.},
\citet{torres_modeling_2011,morton_efficient_2012,diaz_pastis_2014,santerne_pastis_2015,morton_false_2016}
and \citet{giacalone_triceratops_2020}.  ``Validation'' is different
from ``confirmation'', which means that there is overwhelming evidence
that the transits {\it must} be explained by a planet, through
elimination of all false positive scenarios and determination that the
planety's mass is in the substellar regime.

@@

\subsubsection{Not SB2}
We determined our detection limits to blended spectroscopic companions
using the stacked CHIRON spectra (see Section~\ref{subsec:chiron}).  For a
slowly rotating stellar companion well-separated in velocity, this
would have revealed companions with flux fractions $F_2/F_1 \gtrsim
3\%$.  For a companion with rotational broadening of $15\,{\rm
km\,s}^{-1}$, roughly equivalent to that of \tn, we were able to
exclude companions with flux fractions exceeding $\approx$8\%.  For
plotting purposes, in Figure~\ref{fig:fpscenario} we have assumed the
latter flux-fraction limit of 8\% ($\Delta {\rm mag} \approx 2.7$).
For bound companions this is justified through reasoning that coeval
binary companions to \tn\ would have both longer rotation periods and
smaller stellar radii. The equatorial velocities of such companions
would therefore be expected to be smaller than that of \tn.

@@

% timmy.drivers.oneoff_drivers.get_mass_upper_limit
For the first fit we set a prior on the period and
time of periapse using the known ephemeris from the transit.  We then
fitted for the semi-amplitude, instrument offsets, and jitter
parameters.  This yielded a non-detection of the planet's orbit.  The
corresponding 3-$\sigma$ (99.7$^{\rm th}$ percentile) upper limit on
$M_{\rm p} \sin i$ is $1.20 M_{\rm Jup}$.  The data and corresponding
model are shown in Figure~\ref{fig:followup}.

The above exercise ruled out the possibility that the observed
eclipses are caused by a stellar-mass object orbiting \tn.  The lack
of a linear radial velocity trend, particularly in the FEROS
data, further constrains the presence of a hierarchical binary system.
Fitting a line to the FEROS velocities, we found that any third body
in the system would need to induce a linear radial velocity trend with
amplitude $|\dot{\gamma}| < 0.82\,{\rm m\,s}^{-1}\,{\rm
day}^{-1}$, at 3-$\sigma$ confidence.  The baseline of the FEROS data
is 253 days; the agreement between the mean Gaia DR2 velocity ($17.44 \pm
0.64\,$\kms) and that from FEROS ($18.0 \pm 0.1$\kms) in theory places
an additional limit on linear trends, since the two observation
epochs are separated by roughly five years.

To place limits on the properties of a possible bound hierarchical companion, we fitted the radial
velocity data for a Keplerian orbit using wide priors on
the semi-amplitude and period: $\log K\ [{\rm m\,s^{-1}}] \sim
\mathcal{U}(1,10^5)$, and $\log P\ [{\rm days}] \sim \mathcal{U}(0.1,
10^{15})$.  We then fitted for the semi-amplitude, period, time of
conjunction, instrument offsets, and jitter parameters.  We converted
the resulting posterior in period and semi-amplitude to minimum mass
and semi-major axis assuming Kepler's third law.  The resulting
3-$\sigma$ limits are shown in Figure~\ref{fig:fpscenario}.

@@

We fitted for the observed depths in different bandpasses using a
similar machinery as described in Section~\ref{subsec:planet}.  We
fitted each ground-based transit individually for the planet-to-star
size ratio, the impact parameter, and a local quadratic trend (the
ephemeris was assumed from an initial fit of only the TESS data).  The
corresponding 2-$\sigma$ lower limits on the transit depths in
Cousins-R and Johnson-B band light curves were 2.82 and 1.77$\,$ppt,
respectively, and are shown in Figure~\ref{fig:groundphot}.
Particularly in our Johnson-B light curve, the transit depth is
correlated with the mean and linear slope of the light curve: a
smaller depth is allowed if the data are fitted with a larger linear
slope and a larger mean.  Our quoted limits marginalize over these
correlations, and the depth measurement itself is nearly Gaussian.

@@

The ``Gaia'' curve in Figure~\ref{fig:fpscenario} combines both
point-source detections from imaging, and sources that show an
astrometric excess.  The curve was interpolated from Figure~4 of
\citet{rizzuto_zeitVIII_2018}.  \tn\ has a RUWE statistic of 1.022,
indicative that there are no obviously present astrometric companions.
The UWE statistic (square-root of the reduced astrometric $\chi^2$) is
1.38, which is consistent with stars of similar brightness and color
\citep[][Appendix A]{lindegren_gaiasoln_2018}.

@@

\texttt{VESPA} calculates the false positive probability for a transit
signal as
\begin{equation}
  {\rm FPP} = 1 - P_{\rm pl},
\end{equation}
where in our case the probability that the signal comes from a planet,
$P_{\rm pl}$, is given by
\begin{align}
  P_{\rm pl} = 
  \frac{
    \mathcal{L}_{\rm pl}\pi_{\rm pl}
  }{
    \mathcal{L}_{\rm pl}\pi_{\rm pl} + \mathcal{L}_{\rm BEB}\pi_{\rm BEB}
  },
\end{align}
where $\mathcal{L}_i$ is the model likelihood for the planet and BEB
scenarios, and $\pi_i$ is the model prior.  The terms labeled as
``BEB'' usually include other false positive scenarios (HEBs and EBs),
but our followup data have excluded these possibilities.  The priors
are evaluated using a combination of galactic population synthesis
\citep{girardi_star_2005}, binary star statistics
\citep{raghavan_survey_2010}, and specific planet occurrence rates
\citep[][Section~3.4]{morton_efficient_2012}.  The likelihoods are
evaluated by forward-modeling a representative population of
eclipsing bodies for model class, in which each population member has
a particular trapezoidal eclipse depth, total duration, and ingress
duration.  The likelihood is then calculated by multiplying the
probability distribution function of simulated population's shape
parameters with the posterior probability of the actual observed
eclipse shape.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
  {\bf Hertzsprung-Russell diagram of \tn\ and members of \cn.}
  Members (black circles) were identified by
  \citet{cantatgaudin_gaia_2018}.  Gray circles are non-member stars
  within 5 standard deviations of the mean \cn\ right ascension,
  declination, and parallax.  $G$ denotes Gaia broadband magnitudes,
  $Bp$ Gaia blue, and $Rp$ Gaia red.  MIST isochrones (colored lines)
  fit the upper main sequence well, but diverge from the data for
  $M_\star \lesssim 0.7 M_\odot$. This is a known issue with the
  M dwarf models (see Section~\ref{subsec:hr}).
  \label{fig:hr}
	}
\end{figure}

>>>>

\title{
  Cluster Difference Imaging Photometric Survey (CDIPS) II.
  TOI~837: A Young Validated Planet in IC~2602
}

@@

Finding and studying systems undergoing these evolutionary changes is
a major goal in contemporary exoplanet research.  To identify stars
younger than say 1$\,$Gyr, a number of direct and indirect methods are
available \citep{soderblom_ages_2010}.  The traditional approach is to
isochronally age-date coeval groups of stars, hereafter ``clusters''
\citep[{\it
e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
Young field stars can also be identified isochronally, provided that
they are sufficiently massive \citep{berger_gaia-kepler_2020}.  Other
age indicators include stellar rotation periods, the abundance of
photospheric lithium, and chromospheric diagnostics such as calcium
emission and broadband UV emission.  Studies by, for instance,
\citet{david_discovery_2018} and G{.}~Zhou et al{.}~(2020, submitted)
have combined these methods to age-date individual field stars hosting
transiting planets.  Many of these latter methods were summarized by
\citet{mamajek_improved_2008}, and have since been calibrated by, {\it
e.g.},
\citet{irwin_rotational_2009,barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
and \citet{curtis_tess_2019} for stellar rotation,
\citet{zerjal_chromospherically_2017} for chromospheric activity, and
{\it e.g.}, \citet{berger_identifying_2018} and
\citet{zerjal_galah_2019} for lithium abundances.

@@

The discoveries made by K2 through its surveys of Taurus, the Hyades,
Praesepe, and Upper Sco were a major inspiration for the present work
\citep[{\it
e.g.},][]{Mann_K2_25_2016,obermeier_k2_2016,Mann_et_al_2017,vanderburg_zeitVII_2018,ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018,rizzuto_zeitVIII_2018,livingston_k2-264_2019}.
Observations with K2 convincingly showed that at least some close-in
planets must form within about 10 Myr
\citep{Mann_K2_33b_2016,David_et_al_2017}.  They also led to the first
hints that young planets in clusters may in fact be qualitatively
different from their field counterparts.  For instance, based on its
observed mass, radius, and UV environment, the 700$\,$Myr K2-100b is
probably actively losing its atmosphere, and should become a bare
rocky planet over the next few hundred Myr
\citep{Mann_et_al_2017,barragan_radial_2019}.  The four transiting
planets around V1298~Tau (23$\,$Myr) are also likely to be
photoevaporating, and could represent a precursor to Kepler's compact
multiple systems \citep{david_four_2019,david_warm_2019}.

With the aim of advancing the young planet census, we have been using
data from the TESS spacecraft \citep{ricker_transiting_2015} to
perform a Cluster Difference Imaging Photometric Survey
\citep[CDIPS;][]{bouma_cluster_2019}.  Our targets in this survey are
candidate young stars that have been reported in the literature.  At
the time of writing, we had made $\sim$$6\times10^5$ light curves from
the first year of TESS observations. The light curves are available at
MAST\footnote{\stscilink, and see \datasetlink}.  Searching through a
subset of these light curves brought our attention to the candidate
transiting planet, \pn, that is the subject of this analysis.

The transits of \pn\ are grazing, which is a cause for concern.
Particularly for a target near the galactic plane ($b=-5.8^\circ$),
background eclipsing binaries are a major source of astrophysical
false positives \citep[{\it e.g.},][Figure~30]{Sullivan_2015}.  Our
follow-up data show that this and related scenarios are unlikely to
the degree that we can ``validate'' the planet, {\it i.e.}, determine
that its probability of being an astrophysical false positive is
negligibly small.  We considered this result worth reporting because
of the planet's youth.

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.77\textwidth]{f2a.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf TESS light curve of \tn.}
    {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Starspot-induced variability is the dominant signal; flares are
    shown with red crosses.  Dashed lines indicate the five transits
    observed by TESS over Sectors 10 and 11.  {\it Middle}: Individual
    transits.  Gray lines are the best-fit transit model, which
    includes a local quadratic trend in each window. Gray points are
    2-minute \texttt{PDCSAP} flux measurements, black points are
    binned to 15-minute intervals.  {\it Bottom}: Phase-folded TESS
    transit.  Gray points are 2-minute measurements with the local
    spot-induced variation removed.  Binning at 6-minute intervals
    yields the black points.  The black error-bar shows the median
    uncertainty for the black points.  The gray line shows the
    best-fit model to the TESS data. 
		\label{fig:tessphot}
	}
\end{figure*}

@@

The TESS project detected the transits in the 2-minute data and the
community was alerted on 17 June 2019.  Our subsequent blind search of
the CDIPS FFI light curves also showed the transits. Given that the
2-minute data had better sampling cadence, we opted to use the
Presearch Data Conditioning (PDC) light curve with the default
aperture for our
analysis~\citep{smith_kepler_2012,stumpe_multiscale_2014,jenkins_tess_2016,smith_finding_2016}.

@@

The Gaia imaging, reduced to its point-source catalog, provides the
initial context for analyzing the TESS data.  Stars brighter than
$T=16$, as queried from the Gaia DR2 source catalog, are shown with
white circles in Figure~\ref{fig:scene}, overlaid on the TESS image.
Given its galactic latitude of $b=-6^\circ$, it is not surprising that
the field of \tn\ is crowded.  The resolved stars that were of
immediate concern for our false positive analysis were as follows.
\begin{itemize}
  %
  \item \tn\ $\equiv$ TIC 460205581 ($T=9.9$). The target star.
  %
  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3''$ West. The
    proper motions and parallax of this star imply it is co-moving with
    \tn\ and that the two stars are separated by $6.6\pm 0.1\,{\rm pc}$.
    Star A is therefore likely an \cn\ member, but unlikely to be a bound
    binary companion.
  %
  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4''$ North.  The
    Gaia parallax implies this is a background giant star.
\end{itemize}
An additional source, TIC 847769581, is $4.9''$ from the target, but
too faint ($T=18.8$) to be the source of the observed transit signal.

@@

At the $\approx1'$ resolution of the TESS data, if either Star A or
Star B were eclipsing binaries, they could be the sources of the
transit signal.  A detailed analysis of ground-based seeing-limited
photometry was necessary to assess and rule out this possibility
(Section~\ref{subsec:groundphot} and Figure~\ref{fig:groundphot}).

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.49\textwidth]{f2b.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Ground-based follow-up photometry.} The data were acquired
    using the 0.36$\,$m at El Sauce and the 0.40$\,$m ASTEP400 at Dome
    C.  Black points represent the measurements after binning at
    10-minute intervals. The gray line is the model that best fits the
    combined TESS and ground-based data.  Red and blue lines show
    2-$\sigma$ lower limits on the transit depths in the Cousins-R and
    Johnson-B bandpasses used to rule out specific false positive
    scenarios (see Section~\ref{subsec:colorphot}).
		\label{fig:groundphot}
	}
\end{figure}

@@

\tn\ was observed with ASTEP on 12 May 2020, 29 May 2020, 14 June
2020, and 23 June 2020 (UT) with a cadence of $50\,$s (exposure time
of $25\,$s, readout and processing overhead of $25\,$s).  Except for
12 May, our observations were conducted under stable weather
conditions, with clear skies, temperatures of about $-70^\circ$C, and
wind speeds less than 5\,m$\,$s$^{-1}$. Due to their poor quality, we
exclude from the analysis all data collected on May 12. We found that
the optimal calibrated light curves of \tn\ correspond to an 11 pixel
(10\,arcsec) and 14 pixel (12\,arcsec) radius aperture for
observations carried out on June and May, respectively.  The data are
reported in Table~\ref{tab:phot}, and plotted in
Figure~\ref{fig:groundphot}.

@@

The spectroscopic line profiles were thoroughly examined for any signs
of secondary lines that might indicate the presence of another star,
either associated or in chance alignment with TOI 837. No such set of
lines were found. To set limits on the contributions of a close-by
star to the observed spectrum, we injected a second set of lines to
the mean least-squares deconvolution profile derived from the CHIRON
observations. The injection spanned 10,000 different combinations of
line broadening, velocity separation, and flux ratio $F_2/F_1$. The
recovery results showed that for rotational broadenings of the
secondary of $5$, $15$, and $25\,\mathrm{km\,s}^{-1}$, we were able to
exclude sources with flux fractions $F_2/F_1$ brighter than roughly
$0.03$, $0.08$, and $0.20$, provided that the secondary was separated
from the primary by at least $\approx 15\,{\rm km\,s}^{-1}$.  At
smaller velocity separations, the injected lines begin to blend with
the target spectrum.

\subsubsection{FEROS}
TOI 837.01 was monitored with the FEROS echelle spectrograph
\citep{kaufer_commissioning_1999}, mounted on the MPG 2.2$\,$m
telescope at the ESO La Silla Observatory, in Chile. FEROS has a
resolution of $\approx$48,000 across a spectral range of 350–920 nm.
It has a remarkably high efficiency of $\approx$20\%. We obtained 13
spectra of \tn\ between July 5 of 2019 and March 14 of 2020 in the
context of the Warm gIaNts with tEss (WINE) collaboration, which
focuses on the systematic characterization of TESS transiting giant
planets with moderately long orbital periods \citep[{\it
e.g.},][]{brahm:2019,jordan:2020}.  We adopted exposure times of 500
and 600 seconds and the observations were performed with the
simultaneous calibration mode for tracing the instrumental velocity
variations with a comparison fiber illuminated with a ThAr lamp. FEROS
data was processed with the \texttt{ceres} pipeline
\citep{brahm_2017_ceres}, which delivers precision radial velocities
and bisector span measurements through cross-correlation of the
extracted spectra with a binary mask resembling the properties of a
G2V star. The radial velocities are given in Table~\ref{tab:rvs}, and
shown in Figure~\ref{fig:followup}.
To check for the presence of secondary lines, we performed a similar
injection-recovery exercise as with the CHIRON data. 
We achieved slightly worse limits, likely due to the lower spectral
resolution of FEROS, and therefore adopted the CHIRON limits.

@@

Validating a transiting planet means statistically arguing that the
data are much more likely to be explained by a planet than by an
astrophysical false positive. The concept of validation has been
developed and calibrated by {\it e.g.},
\citet{torres_modeling_2011,morton_efficient_2012,diaz_pastis_2014,santerne_pastis_2015,morton_false_2016}
and \citet{giacalone_triceratops_2020}.  ``Validation'' is different
from ``confirmation'', which means that there is overwhelming evidence
that the transits {\it must} be explained by a planet, through
elimination of all false positive scenarios and determination that the
planet's mass is in the substellar regime.

@@

\subsubsection{Not SB2}
We derived limits on blended spectroscopic companions using the
stacked CHIRON spectra (see Section~\ref{subsec:chiron}).  For a
slowly rotating stellar companion well-separated in velocity, the
spectra would have revealed companions with flux fractions $F_2/F_1
\gtrsim 3\%$.  For a companion with rotational broadening of $15\,{\rm
km\,s}^{-1}$, roughly equivalent to that of \tn, we were able to
exclude companions with flux fractions exceeding $\approx$8\%.  For
plotting purposes, in Figure~\ref{fig:fpscenario} we have assumed the
latter flux-fraction limit of 8\% ($\Delta {\rm mag} \approx 2.7$).
% For bound companions this is justified through reasoning that coeval
% binary companions to \tn\ would have both longer rotation periods and
% smaller stellar radii. The equatorial velocities of such companions
% would therefore be expected to be smaller than that of \tn.

@@

% timmy.drivers.oneoff_drivers.get_mass_upper_limit
For the first fit we set a prior on the period and
time of conjunction using the known ephemeris from the transit.  We then
fitted for the semi-amplitude, instrument offsets, and jitter
parameters.  This yielded a non-detection of the planet's orbit.  The
corresponding 3-$\sigma$ (99.7$^{\rm th}$ percentile) upper limit on
$M_{\rm p} \sin i$ is $1.20 M_{\rm Jup}$.  The data and corresponding
model are shown in Figure~\ref{fig:followup}.

The above exercise ruled out the possibility that the observed
eclipses are caused by a stellar-mass object orbiting \tn.  The lack
of a linear radial velocity trend, particularly in the FEROS data,
further constrains the presence of a hierarchical binary system.
Fitting a line to the FEROS velocities yielded a 3-$\sigma$ limit on
linear radial velocity trends of $|\dot{\gamma}| < 0.82\,{\rm
m\,s}^{-1}\,{\rm day}^{-1}$, over the 253 day FEROS baseline.  The
agreement between the mean Gaia DR2 velocity ($17.44 \pm 0.64\,$\kms)
and that from FEROS ($18.0 \pm 0.1$\kms) in theory places an
additional limit on linear trends, since the two observation epochs
are separated by roughly five years.

To place limits on the properties of a possible bound hierarchical
companion, we fitted the radial velocity data for a Keplerian orbit
assuming wide logarithmic priors on the semi-amplitude and period:
$K\ [{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^5)$, and $P\ [{\rm
days}] \sim \log \mathcal{U}(0.1, 10^{15})$.
We then fitted for the semi-amplitude, period, time of conjunction,
instrument offsets, and jitter parameters.  We converted the resulting
posterior in period and semi-amplitude to minimum mass and semi-major
axis assuming Kepler's third law.  The resulting 3-$\sigma$ limits are
shown in Figure~\ref{fig:fpscenario}.

@@

We fitted for the observed depths in different bandpasses using a
machinery similar to that described below in Section~\ref{subsec:planet}.  We
fitted each ground-based transit individually for the planet-to-star
size ratio, the impact parameter, and a local quadratic trend (the
ephemeris was assumed from an initial fit of only the TESS data).  The
corresponding 2-$\sigma$ lower limits on the transit depths in
Cousins-R and Johnson-B band light curves were 2.82 and 1.77$\,$ppt,
respectively, and are shown in Figure~\ref{fig:groundphot}.
Particularly in our Johnson-B light curve, the transit depth is
correlated with the mean and linear slope of the light curve: a
smaller depth is allowed if the data are fitted with a larger linear
slope and a larger mean.  Our quoted limits marginalize over these
correlations, and the depth measurement itself is nearly Gaussian.

@@

The ``Gaia'' curve in Figure~\ref{fig:fpscenario} combines both
point-source detections from imaging and sources showing an
astrometric noise excess relative to the single-source astrometric
model.  The curve was interpolated from Figure~4 of
\citet{rizzuto_zeitVIII_2018}.  \tn\ has a RUWE statistic of 1.022,
indicative that there are no obviously present astrometric companions.
The UWE statistic (square-root of the reduced astrometric $\chi^2$) is
1.38, which is consistent with stars of similar brightness and color
\citep[][Appendix A]{lindegren_gaiasoln_2018}.

@@

\texttt{VESPA} calculates the false positive probability for a transit
signal as
\begin{equation}
  {\rm FPP} = 1 - P_{\rm pl},
\end{equation}
where in our case the probability that the signal comes from a planet,
$P_{\rm pl}$, is given by
\begin{align}
  P_{\rm pl} = 
  \frac{
    \mathcal{L}_{\rm pl}\pi_{\rm pl}
  }{
    \mathcal{L}_{\rm pl}\pi_{\rm pl} + \mathcal{L}_{\rm BEB}\pi_{\rm BEB}
  },
\end{align}
where $\mathcal{L}_i$ is the model likelihood for the planet and BEB
scenarios, and $\pi_i$ is the model prior.  The terms labeled as
``BEB'' usually include other false positive scenarios (HEBs and EBs),
but our followup data have excluded these possibilities.  The priors
are evaluated using a combination of galactic population synthesis
\citep{girardi_star_2005}, binary star statistics
\citep{raghavan_survey_2010}, and specific planet occurrence rates
\citep[][Section~3.4]{morton_efficient_2012}.  The likelihoods are
evaluated by forward-modeling a representative population of eclipsing
bodies for each model class, in which each population member has a
particular trapezoidal eclipse depth, total duration, and ingress
duration.  The likelihood is then calculated by multiplying the
probability distribution function of the simulated population's shape
parameters with the posterior probability of the actual observed
eclipse shape.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
  {\bf Hertzsprung-Russell diagram of \tn\ and members of \cn.}
  Members (black circles) were identified by
  \citet{cantatgaudin_gaia_2018}.  Gray circles are non-member stars
  with right ascension, declination, and parallax similar to \cn.
  They are selected by drawing from a $(\alpha, \delta, \pi)$ cube
  centered on the cluster with boundaries set at $5\times$ the
  standard deviation in the cluster parameters.  $G$ denotes Gaia
  broadband magnitudes, $Bp$ Gaia blue, and $Rp$ Gaia red.  MIST
  isochrones (colored lines) fit the upper main sequence well, but
  diverge from the data for $M_\star \lesssim 0.7 M_\odot$. This is a
  known issue with the M dwarf models (see Section~\ref{subsec:hr}).
  \label{fig:hr}
	}
\end{figure}

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.65\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{ 
  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black
  circles), and stars in the neighborhood (gray circles).} Members
  were identified by \citet{cantatgaudin_gaia_2018}. 
  Neighbors are as in Figure~\ref{fig:hr}. $\alpha$ denotes
  right ascension, $\delta$ declination, $\pi$ parallax, $\mu_{\rm
  \delta}$ and $\mu_{\rm \alpha}$ proper motion in each equatorial
  direction, and ${\rm RV}$ radial velocity reported by Gaia DR2.  The
  RVs are for unblended spectra of bright stars ($G\lesssim 12$).  The
  proper motion projection ($\mu_{\delta}$ vs{.} $\mu_{\rm
  \alpha}\cos\delta$) highlights incompleteness in the membership
  selection function.
  \label{fig:full_kinematics}
	}
\end{figure*}
